Combining global tree cover loss data with historical national forest cover maps to look at six decades of deforestation and forest fragmentation in Madagascar

### 2018-03-16 manuscript/manuscript.Rnw
Arrange text

Original 1990-2000 forest cover change map for Madagascar from
\citet{Harper2007} is a raster map at 28.5 m resolution. It was
derived from the supervised classification of Landsat TM (Thematic Mapper) and 
ETM+ (Enhanced Thematic Mapper Plus) satellite images. For our study, this map 
has been resampled at 30~m resolution 
using a nearest-neighbor interpolation and reprojected in the WGS 84/UTM zone 
38S projected coordinate system.

@@

The 1973 forest cover map for Madagascar from \citet{Harper2007} is a 
raster map at 57 m resolution derived from the supervised classification of 
Landsat MSS (Multispectral Scanner System) satellite images. We resampled this 
map at 30~m resolution using a nearest-neighbor interpolation on the same grid 
as the forest cover maps for years 1990 and 2000. We completed the Harper's 
forest map of year 1973 by filling unclassified areas using our forest cover 
map of the year 1990 assuming that if forest was present in 1990, it was also
present in 1973. Contrary to the year 1990, the remaining unclassified
pixels for year 1973 corresponded to a significant total area of 3.3
millions ha which was left as is.

The 1953 forest cover map from \citet{Harper2007} is a vector map produced by scanning 
the paper map of \citet{Humbert1965} which was derived from the visual interpretation 
of aerial photographs. We reprojected the forest cover map of year 1953 in the WGS 84/UTM zone 
38S projected coordinate system. Because of the methodology used to derive the 1953 forest 
cover map, it was not possible to perfectly aligned this map with the forest cover 
maps of later years which were produced through digital processing of satellite imagery. 
As a consequence, the 1953 cannot be merged with the map of later years to identify 
precisely the location of the deforested areas. Nonetheless, the 1953 forest cover 
map can be used to have a rough estimate of the forest cover and forest fragmentation at this date.
To do so, the map was rasterized at 30 m resolution on the same grid 
as the forest cover maps for years 1973, 1990 and 2000.

Finally for all forest cover maps from 1973, isolated single non-forest pixels
(i.e.~fully surrounded by forest pixels) were recategorized as forest pixels.
Doing so, forest cover increased from about 95,000 ha for year 1953 to
about 600,000 ha for year 2010. This allowed us to avoid counting very small scale
events (\textless 0.1 ha, such as selective logging or wind-throw) as
deforestation. It also prevents us from underestimating forest cover and overestimating 
forest fragmentation. All the resulting maps have been made permanently and
freely available on the Zenodo research data repository at
\url{https://doi.org/10.5281/zenodo.1145785}.

>>>>

Original 1990-2000 forest cover change map for Madagascar from
\citet{Harper2007} is a raster map at 28.5~m resolution. It was
derived from the supervised classification of Landsat TM (Thematic
Mapper) and ETM+ (Enhanced Thematic Mapper Plus) satellite images. For
our study, this map has been resampled at 30~m resolution using a
nearest-neighbor interpolation and reprojected in the WGS 84/UTM zone
38S projected coordinate system.

@@

The 1973 forest cover map for Madagascar from \citet{Harper2007} is a
raster map at 57~m resolution derived from the supervised
classification of Landsat MSS (Multispectral Scanner System) satellite
images. We resampled this map at 30~m resolution using a
nearest-neighbor interpolation on the same grid as the forest cover
maps for years 1990 and 2000. We completed the Harper's forest map of
year 1973 by filling unclassified areas using our forest cover map of
the year 1990 assuming that if forest was present in 1990, it was also
present in 1973. Contrary to the year 1990, the remaining unclassified
pixels for year 1973 corresponded to a significant total area of 3.3
millions ha which was left as is.

The 1953 forest cover map from \citet{Harper2007} is a vector map
produced by scanning the paper map of \citet{Humbert1965} which was
derived from the visual interpretation of aerial photographs. We
reprojected the forest cover map of year 1953 in the WGS 84/UTM zone
38S projected coordinate system. Because of the methodology used to
derive the 1953 forest cover map, it was not possible to perfectly
aligned this map with the forest cover maps of later years which were
produced through digital processing of satellite imagery. As a
consequence, the 1953 cannot be merged with the map of later years to
identify precisely the location of the deforested areas. Nonetheless,
the 1953 forest cover map can be used to have a rough estimate of the
forest cover and forest fragmentation at this date.  To do so, the map
was rasterized at 30~m resolution on the same grid as the forest cover
maps for years 1973, 1990 and 2000.

Finally for all forest cover maps from 1973, isolated single
non-forest pixels (i.e.~fully surrounded by forest pixels) were
recategorized as forest pixels.  Doing so, forest cover increased from
about 95,000~ha for year 1953 to about 600,000~ha for year 2010. This
allowed us to avoid counting very small scale events (\textless 0.1
ha, such as selective logging or wind-throw) as deforestation. It also
prevents us from underestimating forest cover and overestimating
forest fragmentation. All the resulting maps have been made
permanently and freely available on the Zenodo research data
repository at \url{https://doi.org/10.5281/zenodo.1145785}.
